---
title: "A collection of financial data found online"
output: html_notebook
---

```{r setup}

knitr::opts_chunk$set(warning = FALSE, message = FALSE)  

library(tidyverse)
library(readxl)
library(haven)
library(httr)

```


# Maddison Project

[Maddison project](https://www.rug.nl/ggdc/historicaldevelopment/maddison/releases/maddison-project-database-2018) is good source for very long data series. 

```{r madison}

# Download Madison original works in Excel-format. URL refuse to work directly in readxl.
# Use httr to download file

httr::GET("https://www.rug.nl/ggdc/historicaldevelopment/maddison/data/mpd_2013-01.xlsx", 
   httr::write_disk("mpd_2013-01.xlsx"))

# Import data, 
# skip the to first rows, 
# clean the first header name and make the data in tidy format.

maddision2013 <- read_xlsx("mpd_2013-01.xlsx", skip = 2) %>% 
  rename(Year = 1) %>%
  pivot_longer(-Year, names_to = "Country", values_to = "GDP")

# 2013 data is still quite messy. 
# Must review which variable to use (e.g. various sub-totals present)

# 2018 edition. Looks similiar to the first, but with much more and cleaner data. 

maddison2018 <- haven::read_dta("https://www.rug.nl/ggdc/historicaldevelopment/maddison/data/mpd2018.dta")

# Cleaner data, but less data than 2018 edition. 

maddison2020 <- haven::read_dta("https://www.rug.nl/ggdc/historicaldevelopment/maddison/data/mpd2020.dta")

# 2018, 2020 data already in tidy format. Enjoy. 

```


# Macrohistory.net

[Macrohistory](https://www.macrohistory.net/database/) provides long historical data. 


```{r macrohistory}

macrohistory <- haven::read_dta("http://data.macrohistory.net/JST/JSTdatasetR5.dta")

```


# Investor Amnesia

[Investor Amnesia](https://investoramnesia.com/historical-data/) provides for the purpose data. Importing data depends on source and some require manual downlowds. No script at the moment. 

# Kenneth French Data Library

[Kenneth French](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html) is a pioneer in factor investing. There are many return sources, thus find the one that fits the bill. 


